Simulation Tables

### 2019-07-01 manuscript/manuscript.tex
section 3

\textbf{\textit{Put lit review of Bayesian PG multinomial logistic regression here}}

>>>>

Polson et al. (2013) introduce a data augmentation scheme using the P\'olya-Gamma distribution which allows for sampling of multinomial regression parameters using straightforward Gibb's updates from Gaussian full conditional distributions. In addition to more convinient parameter estimation, the P\'olya-Gamma data augmentation method for logistic regression has the advantage of direct sampling from the posterior distributions of multinomial parameters. This approach avoids the need for approximations of the posterior distribution, thus yeilding more stable sampling, especially when the number of parameters approaches the number of observations (Polson et al., 2013). P\'olya-Gamma data augmentation for multinomial regression has not yet been applied to the analysis of longitudinally clustered data.

### 2019-07-01 mcmc_draws_2019-07-01/tables.Rmd
section 3

```{r}
setwd("~/Documents/School/Summer_2019/Research/MVSN-FMM/mcmc_draws_2019-06-27")
load("BETA")
load("beta_true")
load("DELTA")
load("delta_true")
load("PI")
load("PSI")
load("psi_true")
load("SIGMA")
load("sig2_true")
load("pi_true")
load("Z")
```

>>>>

```{r}
setwd("~/Documents/School/Summer_2019/Research/MVSN-FMM/mcmc_draws_2019-07-01")
load("BETA")
load("beta_true")
load("DELTA")
load("delta_true")
load("PI")
load("PSI")
load("psi_true")
load("SIGMA")
load("sig2_true")
load("pi_true")
load("Z")
```
